\vspace{-1.75cm}Ph.D. Proposal

### 2022-05-15 abstract/abstract.tex
correzione grammatica

\documentclass[a4paper,11pt, oneside]{article}
\usepackage[left=15mm, right=15mm, top=15mm, bottom=15mm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{framed}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[tickmarkheight=0.7ex]{todonotes}
\newcommand{\gdv}[1]{\todo{\textbf{GDV} #1}}
\newcommand{\pb}[1]{\todo{\textbf{PB} #1}}
\newcommand{\dc}[1]{\todo{\textbf{DC} #1}}
\usepackage[style=numeric, sorting=none, doi=false, isbn=false, url=false,
eprint=false,maxcitenames=2, mincitenames=1, maxbibnames=2, minbibnames=2,
giveninits=true]{biblatex} 
\addbibresource{abstract.bib}

@@

\title{\vspace{-1.75cm}PhD Proposal}
\author{Davide Cozzi, 829827,
  \href{mailto:d.cozzi@campus.unimib.it}{d.cozzi@campus.unimib.it}} 
\date{}
\makeatletter
\renewcommand{\paragraph}{%
  \@startsection{paragraph}{4}%
  {\z@}{0.75ex \@plus 1ex \@minus .2ex}{-1em}%
  {\normalfont\normalsize\bfseries}%
}
\makeatother

@@

to analyze a large collection of individual genomes.  Unfortunately, in 
order to complete these types of studies on a large amount of data, such data

@@

has a size of $\sim 3.1$\textit{gb} and contains $\sim 59,265$ genes, as

@@

\textbf{structural variants}, involving more than 50 nucleotides. Moreover it is
necessary to consider that the objective is the sequencing of at least 100

@@

has linear solution in time, if there is a proper indexing of the text. The

@@

to these algorithms and to the fact that it is retunerd an interval over the

@@

linear on the length of pattern. The

@@

\textbf{BLAST}, based of the \textit{seed-and-extend paradigm}, where short
strings, the so-called \textit{seed}, are choosen to be the starting point of
the alignment. Then, from the seed, the algorithm proceed to extend the match in
order to compute the alignment, increasing the efficiency of the algorithm. The
key point is the ability to compress large texts and to query the compressed
texts themselves.\\  

@@

samples from the same specie. In fact, the need to take into 

@@

%\pb{the main focus of this project proposal is...}
%\pb{IO menzionerei il tempo di calcolo del pattern matching del pattern ad un
%testo che è lineare nel pattern se vi è una adeguata rappresentazione o
%indicizzazione del testo} OK

@@

% progetto...} CIRCA OK

@@

% graphs as I will discuss in the specific goals of my project...} OK

@@

to produce sequences of ever higher quality in less and less time, the

@@

for collection of sequences. In 2021, Rossi et al. proposed \textit{MONI} as a

@@

genomes as a reference \cite{moni}. With this type of encoding, it is possibile

@@

authors used the concept of \textbf{matching statistics (\textit{MS})} in order

@@

  queries}, achieving the same results of \textit{MONI} with only a single sweep
over \textit{MS} array instead of two as in MONI (details in the next section).

@@

biology has led to the development and implementation of algorithms and data

@@

the genotype is their combined information. So, from 2005, publication of the

@@

example in order to study outcomes of diseases.  In this particular historical

@@

replicate a lot but often in a not perfect way, during infections. Thus produces

@@

One of the most important data structure, developed in order to handle the study
of haplotypes sequences, is the \textbf{positional Burrows-Wheeler transform
  (\textit{PBWT})}, proposed by Durbin in 2014 \cite{pbwt_durbin}. \textit{PBWT}

@@

memory by \textit{PBWT} is nearly six times smaller than the raw data. Without
these spatial results it would has been impossible to process real information.

@@

example, in order to extract common patterns in a set of haplotypes. Thanks to

@@

softwares for the study of haplotypes and in various genotype imputation methods

@@

% During the development of my master thesis, I worked to create a run length

@@

% \pb{di in sintesi cosa è l'idea del run length encoding e sopra direi cha la

@@

% In this context, my PhD is going to be focused on the development of new

@@

  structure}.  
A \textit{bitvector} is an array on $n$ bits which allows two particular

@@

function} allows to calculate how many occurrences of one are up to a certain
index. Instead, the \textit{select function} allows to obtain the index of every

@@

From a theoretical point of view these two operations can be supported in

@@

  bitvector, sparse bivector} etc$\ldots$) within \textbf{SDSL (\textit{Succint

@@

for analysis of biological sequences. An example of the use of is 

@@

\textit{PBWT}, where we put one at each head of run, allowing fast operations
for indexing and mapping. 

@@

\paragraph*{Run length encoding and succinct data structures.}
% \pb{Run length encoding and succinct data structures... potrebbe essere il

@@

in 1994 in order to compress texts but it has been used widely

@@

$T$, $RLBWT_T$ is a rappresentation of $BWT_T$ with a compact storage of

@@

the text, $n$, to being linear over the number of runs, $r$, so sub-linear over

@@

at the beginning and at the end of every run. The algorithm for querying through

@@

  query}, given two position $i$ and $j$ in a text $T$, such that $|T|=n$,

@@

between two position in the text. Both solutions operate on a compressed

@@

\textbf{straight-line program (\textit{SLP})}. Briefly an \textit{SLP} is based

@@

and here it is used for \textit{random access} and for \textit{LCE queries}. 
The purpose of the two projects is computation of the \textbf{matching

@@

function called $\varphi$ (and and its inverse $\varphi^{-1}$), based on the use

@@

\textbf{positional Burrows–Wheeler transform (\textit{PBWT})}, in order to

@@

index of the haplotype $m$ in the original panel, for each column $k$ and for  

@@

software making genotype imputation in order to predict unobserved genotypes
from a panel with milions of haplotypes, so it was necessary to use
\textit{PBWT}. Improving this data structure, it will be possibile to help the

@@

systems biology. So, it is my interest to continue my studies with the PhD
in order to be able to deepen the computer science potential in the biological

@@

Summarizing, the most important research goal of my PhD is designing and

@@

  grow, as well as the number of sample (even if there is only a 2\% presence of

@@

  usually not considered by the majority of tools. A first step in this

@@

  Talking about spatial complexity, run-length encoded version of the stored

@@

  although now they have really high correctness rates. Unfortunately, this is

@@

  based on researches already developed in \textit{BIAS}.
  \item \textbf{Algorithms for pangenome graph \& other goals}. Another research

@@

  the study of \textit{pangenome graph}. In fact, it is possibile to interpret

@@

  pangenome graph, in a compact way via the \textbf{Graph BWT (\textit{GBWT})},

@@

  improvement would be a spatial optimization. There are a lot of open problems 
  regarding the use of \textit{GBWT}, such as handling missing / erroneous data

@@

  for the \textit{GBWT}, because it would be possibile to

@@

  pattern matching, indexing structures and pangenome graph, according to the

@@

  % and develop during my PhD. The management of missing and

@@

some technologies that will be used during my PhD must be mentioned. 
During both my bachelor and master degree, I mainly focused on the use of the
\textbf{C++ programming language}, thanks to the

@@

%     eventualmente approfondito durante il PhD, è praticamente un

>>>>

\documentclass[a4paper,11pt, oneside]{article}
\usepackage[left=15mm, right=15mm, top=15mm, bottom=15mm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{framed}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[tickmarkheight=0.7ex]{todonotes}
\newcommand{\gdv}[1]{\todo[backgroundcolor=blue]{\textbf{GDV} #1}}
\newcommand{\pb}[1]{\todo[backgroundcolor=red]{\textbf{PB} #1}}
\newcommand{\dc}[1]{\todo[[backgroundcolor=yellow]{\textbf{DC} #1}}
\usepackage[style=numeric, sorting=none, doi=false, isbn=false, url=false,
eprint=false,maxcitenames=2, mincitenames=1, maxbibnames=2, minbibnames=2,
giveninits=true]{biblatex} 
\addbibresource{abstract.bib}

@@

\title{\vspace{-1.75cm}Ph.D. Proposal}
\author{Davide Cozzi, 829827,
  \href{mailto:d.cozzi@campus.unimib.it}{d.cozzi@campus.unimib.it}} 
\date{}
\makeatletter
\renewcommand{\paragraph}{%
  \@startsection{paragraph}{4}%
  {\z@}{0.75ex \@plus 1ex \@minus .2ex}{-1em}%
  {\normalfont\normalsize\bfseries}%
}
\makeatother

@@

to analyze a large collection of individual genomes.  Unfortunately, to complete
these types of studies on a large amount of data, such data 

@@

has a size of $\sim 3.1$\textit{Gb} and contains $\sim 59,265$ genes, as

@@

\textbf{structural variants}, involving more than 50 nucleotides. Moreover, it
is necessary to consider that the objective is the sequencing of at least 100

@@

has linear solution in time, if there is proper indexing of the text. The

@@

to these algorithms and to the fact that it is returned an interval over the

@@

linear on the length of the pattern. The

@@

\textbf{BLAST}, based on the \textit{seed-and-extend paradigm}, where short
strings, the so-called \textit{seed}, are chosen to be the starting point of
the alignment. Then, from the seed, the algorithm proceeds to extend the match
to compute the alignment, increasing the efficiency of the
algorithm. The key point is the ability to compress large texts and query the
compressed texts themselves.\\  

@@

samples from the same species. In fact, the need to take into 

@@

% \pb{the main focus of this project proposal is...}
% \dc{Corretto}
% \pb{IO menzionerei il tempo di calcolo del pattern matching del pattern ad un
% testo che è lineare nel pattern se vi è una adeguata rappresentazione o
% indicizzazione del testo}
% \dc{Aggiunto}

@@

% progetto...}
% \dc{Aggiunto in modo sintetico}

@@

% graphs as I will discuss in the specific goals of my project...}
% \dc{Aggiunto}

@@

to produce sequences of ever-higher quality in less and less time, the

@@

for collections of sequences. In 2021, Rossi et al. proposed \textit{MONI} as a

@@

genomes as a reference \cite{moni}. With this type of encoding, it is possible

@@

authors used the concept of \textbf{matching statistics (\textit{MS})}

@@

  queries}, achieving the same results as \textit{MONI} with only a single sweep
over \textit{MS} array instead of two as in \textit{MONI} (details in the next
section). 

@@

biology have led to the development and implementation of algorithms and data

@@

the genotype is their combined information. So, since 2005, publication of the

@@

example to study the outcomes of diseases.  In this particular historical

@@

replicate a lot but often in a not perfect way, during infections. This produces

@@

One of the most important data structures, developed to handle the
study of haplotypes sequences, is the \textbf{positional Burrows-Wheeler
  transform (\textit{PBWT})}, proposed by Durbin in 2014
\cite{pbwt_durbin}. \textit{PBWT} 

@@

memory by \textit{PBWT} is nearly six times smaller than the raw data. These
spatial results are necessary to process real information. 

@@

example, to extract common patterns in a set of haplotypes. Thanks to

@@

software for the study of haplotypes and in various genotype imputation methods

@@

% During the development of my master thesis, I worked to create a run-length

@@

% \pb{di in sintesi cosa è l'idea del run-length encoding e sopra direi cha la

@@

% In this context, my Ph.D. is going to be focused on the development of new

@@

  structures}.  
A \textit{bitvector} is an array on $n$ bits that allows two particular

@@

function} allows calculating how many occurrences of one are up to a certain
index. Instead, the \textit{select function} allows obtaining the index of every

@@

From a theoretical point of view, these two operations can be supported in

@@

  bitvector, sparse bivector}, etc$\ldots$) within \textbf{SDSL (\textit{Succint

@@

for the analysis of biological sequences. An example of the use is 

@@

\textit{PBWT}, where we put one at each head of every run, allowing fast
operations for indexing and mapping. 

@@

\paragraph*{Run-length encoding and succinct data structures.}
% \pb{Run-length encoding and succinct data structures... potrebbe essere il

@@

in 1994 to compress texts but it has been used widely

@@

$T$, $RLBWT_T$ is a representation of $BWT_T$ with a compact storage of

@@

the text, $n$, to be linear over the number of runs, $r$, so sub-linear over

@@

at the beginning and the end of every run. The algorithm for querying through

@@

  query}, given two positions $i$ and $j$ in a text $T$, such that $|T|=n$,

@@

between two positions in the text. Both solutions operate on a compressed

@@

\textbf{straight-line program (\textit{SLP})}. Briefly, an \textit{SLP} is based

@@

and here it is used for \textit{random access} and \textit{LCE queries}. 
The purpose of the two projects is the computation of the \textbf{matching

@@

function called $\varphi$ (and its inverse $\varphi^{-1}$), based on the use

@@

\textbf{positional Burrows–Wheeler transform (\textit{PBWT})}, to

@@

index of the haplotype $m$ in the original panel, for each column $k$ and

@@

software is making \textit{genotype imputation} to predict unobserved
genotypes from a panel with millions of haplotypes, so it was necessary to use
\textit{PBWT}. Improving this data structure, it will be possible to help the

@@

systems biology. So, it is my interest to continue my studies with the Ph.D.
to be able to deepen the computer science potential in the biological

@@

Summarizing, the most important research goal of my Ph.D. is designing and

@@

  grow, as well as the number of sample(even if there is only a 2\% presence of

@@

  usually not considered by the majority of tools. The first step in this

@@

  Talking about spatial complexity, the run-length encoded version of the stored

@@

  although now they have high correctness rates. Unfortunately, this is

@@

  based on research already developed in \textit{BIAS}.
  \item \textbf{Algorithms for pangenome graphs \& other goals}. Another research

@@

  the study of \textit{pangenome graphs}. In fact, it is possible to interpret

@@

  pangenome graphs, in a compact way via the \textbf{Graph BWT (\textit{GBWT})},

@@

  improvement would be spatial optimization. There are a lot of open problems 
  regarding the use of \textit{GBWT}, such as handling missing/erroneous data

@@

  for the \textit{GBWT}, because it would be possible to

@@

  pattern matching, indexing structures and pangenome graphs, according to the

@@

  % and develop during my Ph.D.. The management of missing and

@@

some technologies that will be used during my Ph.D. must be mentioned. 
During both my bachelor's and master's degree, I mainly focused on the use of
the \textbf{C++ programming language}, thanks to the

@@

%     eventualmente approfondito durante il Ph.D., è praticamente un
